**Operating model**

### 2023-03-06 Rmd/report mac.Rmd
report mac

---
output:
  html_document:
    reference_docx: ../report_template.dotx
mathjax: TRUE
bibliography: refs.bib
---

@@

load(file=file.path(dropboxdir,paste0("data/om/",mystk,"/parMat.RData")))
```

@@

```{r, echo=FALSE, out.width = "400px", fig.align="left", message=FALSE, warning=FALSE, cache=FALSE}

@@

```{r}
load("~/Dropbox/DDMSE/data/om/mac/parMat.RData") 
```

>>>>

---
output:
  word_document:
    reference_docx: ../report_template.dotx
mathjax: TRUE
bibliography: refs.bib
---

@@

load(file=file.path(dropboxdir,paste0("data/om/",mystk,"matPar.RData")))
```

@@

@@
